Perimeter Control of Swarms

### 2018-12-20 paper.tex
Initial group tidying up

\section{Introduction}
\section{Related Work}
\section{Baseline specification}
To allow an analysis of each algorithm's effect on a swarm a baseline measurement of `background' variance (jitter) is identified. The baseline measurement provides a comparative data set for the experiments. The baseline data set is for a static swarm (no destination vector) with the same internal parameters.

@@

\begin{center}
\begin{equation}‎
\label{eq:ConcaveVoidPhysics1}
S_b \buildrel \Delta \over =‎ \{(b',\angle\{(b'~b~b^0)) : b' \in nbr(b)\}
\end{equation}‎
\end{center}

Figure~\ref{eq:ConcaveVoidPhysics1} generates the dictionary set of all the neighbours along with an angle that each of the agent's neighbour's make with the first detected neighbour.
%% 
%% \begin{center}
%% \begin{equation}‎
%% \label{eq:ConcaveVoidPhysics2}
%% G_b \buildrel \Delta \over =‎ gap(S_b,\angle<180^\circ)
%% \end{equation}‎
%% \end{center}

@@

\begin{equation}\label{eq:CosineRule1}
z = \sqrt{x^2 + y^2 - 2xy~\cos(\theta)}
\end{equation}‎

@@

\begin{equation}\label{eq:Centroid1}
C_s = \frac{1}{|S|}\mathlarger{\sum_{b' \in S}} b'
\end{equation}‎

@@

\begin{equation}\label{eq:SwarmDistance1}
d = \sqrt{(x_{t}-x_{t^1})^2+(y_{t}-y_{t^1})^2}
\end{equation}‎

\begin{equation}\label{eq:SwarmSpeed1}
S_s = \frac{d}{n}
\end{equation}‎

>>>>

\section{Introduction}\label{sec:Introduction}
\textit{Swarming} in the animal kingdom of ants, bees, fish and birds for instance has long been studied by scientists. From these studies mathematical models and algorithms have evolved. The models and algorithms have in turn captured the interest of computing scientists who are interested in applying them to large groups of autonomous mobile \textit{agents} (`robots'). The cooperative coordination of these agents can take many forms such as following a set path~\cite{HCS:09}, existing in a static space~\cite{EP:10, GP:02, GP:04} or foraging as a colony~\cite{HER:11, GK:07}. One of the attributes of swarms that has captured the interest of scientists is that the models and algorithms used to coordinate them are generally sets of simple rules. These simple rules cause the agents to appear to work cooperatively.
Currently, much swarm research uses field effects as the method of modelling inter-agent interactions~\cite{BAF:06, BAFVM:06, BM:09, APZDAMC:09, GP:02, GP:04, GP:04a, GP:05, GP:11, MYP:09}. The models usually use two \textit{field effects} to implement the swarming characteristic. These effects are \textit{cohesion}, to draw agents closer, and \textit{repulsion} to prevent agents colliding. \textit{Field effects} have ranges around an agent to determine the effect other agents have upon its movement~(Fig.~\ref{methods:FieldEffects}) the effects are derived from these ranges as vectors. All ranges must fall within the sensing capabilities of the agent ($S_b$). It is usual for the cohesion field to have a radius ($C_b$) which is larger than the repulsion radius ($R_b$). When an agent ($b'$) moves into the \textit{neighbour field} of an agent ($b$) then $b'$ is said to be a neighbour of $b$ and is subject to cohesion. When an agent $b'$ moves into the repulsion field of $b$ then $b$ also subjected to repulsion. When the repulsion magnitude exceeds the cohesion magnitude the agent will have a tendency to move away from $b'$, i.e. repelled. When an agent $b$ moves too close to an obstacle, i.e. within the obstacle repulsion range $O_b$, it has its repulsion vector applied and the agent will tend towards moving away from the obstacle.

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt){figures/stableswarm} {Agent field effects.\label{methods:FieldEffects}}

When cohesion and repulsion (\textit{inter-agent vectors}) are the only field effects creating a swarming effect the number of stable structures that can develop is limited. These structures, which are constructed from triangles, are either straight edges or partial lattices. Partial lattices can create concave anomalies (\textit{dents}) and convex anomalies (\textit{peaks}) in a perimeter~(Fig.~\ref{concave:SwarmStableShape1}). An anomaly is any construct within the swarm that is not a hexagonal lattice or an agent distribution that causes the swarm to deviate from having only convex or flat edges. The advantage of creating a well structured swarm can be realised in two classes of swarm application; \textit{Reconnaissance}, by creating a more uniform structure that eliminates blank spots, and \textit{Object Containment}, when using a swarm to surround a target.

\Figure[t!](topskip=0pt, botskip=0pt, midskip=0pt)[width=7.5cm]{figures/SwarmStableShape1}
{Stable swarm edges\label{concave:SwarmStableShape1}}

%% \begin{figure}
%% \begin{center}
%% \includegraphics[width=5cm]{figures/SwarmStableShape1}
%% \end{center}
%% \caption{Stable swarm edges\label{concave:SwarmStableShape1}}
%% \end{figure}
The problem with these anomalies is that, although they are stable due to the balancing of the \textit{inter-agent vectors}, they create non-uniform structures that may be unsuitable for tasks that require a uniform swarm formation.

\textit{Concave reduction} is a form of self-healing, it is a process that creates a movement that makes a swarm coalesce towards a more geometrically stable shape. This is achieved by removing voids and concave edges. The techniques defined in this paper function without the need for inter-agent or global messaging using only local proximity detection.

\section{Related Work}\label{sec:RelatedWork}
Research has identified several approaches to resolving swarm structure issues. A prototype framework for self-healing swarms was developed by Dai et al. which considered the problem of agent failure in hostile environments~\cite{DHMRZ:06}. This is in line with work carried out by Vassev and Hinchey who model swarm deployment using ASSL (Autonomic System Specification Language)~\cite{VH:09}. This technique was used by NASA (National Aeronautics and Space Administration) when developing their ANTS (Autonomous Nano Technology Swarm) for use in asteroid belt exploration. This line of research is more focused towards an agent's internal systems failure rather than the removal of anomalies in a swarm distribution. Roach et al. takes a different approach and focuses on the effects of sensor failure and the effect that has on agent distribution~\cite{RMT:15}. The closest research to concave reduction, as discussed in this paper, is that of Lee and Chong who identify the issue of concave edges within swarms in an attempt to create regular lattice formations~\cite{GN:08}. The main focus of their paper is the restructuring of the internal distribution of inter-agent formations. The research by Ismail and Timmis used the approach of \textit{bio-inspired} healing using \textit{granuloma formation}, a biological method for encapsulating an antigen~\cite{IT:10}. They also consider the effects failed agents can have upon a swarm when traversing a terrain \cite{TIBW:16}. 
Concave reduction is an extension of the work discussed by Ismail and Timmis in their papers on `self-healing' \cite{IT:10} and the effects of failed agents \cite{TIBW:16}. It also builds upon Lee and Chong's work on identifying concave edges~\cite{GN:08}. The technique also draws on the work of McLurkin and Demaine who have developed algorithms to detect perimeter types~\cite{MD:09}. The technique employed in this paper does not require the identification of the perimeter type as this would require a communications infrastructure.
\section{Baseline specification}
To allow an analysis of each algorithm's effect on a swarm a baseline measurement of `background' variance (jitter) is identified. The baseline measurement provides a comparative data set for the experiments. The baseline data set is for a static swarm (no destination vector) with the same internal parameters.

@@

\begin{center}
\begin{equation}
\label{eq:ConcaveVoidPhysics1}
S_b \buildrel \Delta \over = \{(b',\angle\{(b'~b~b^0)) : b' \in nbr(b)\}
\end{equation}
\end{center}

Figure~\ref{eq:ConcaveVoidPhysics1} generates the dictionary set of all the neighbours along with an angle that each of the agent's neighbour's make with the first detected neighbour.
%% 
%% \begin{center}
%% \begin{equation}
%% \label{eq:ConcaveVoidPhysics2}
%% G_b \buildrel \Delta \over = gap(S_b,\angle<180^\circ)
%% \end{equation}
%% \end{center}

@@

\begin{equation}\label{eq:CosineRule1}
z = \sqrt{x^2 + y^2 - 2xy~\cos(\theta)}
\end{equation}

@@

\begin{equation}\label{eq:Centroid1}
C_s = \frac{1}{|S|}\mathlarger{\sum_{b' \in S}} b'
\end{equation}

@@

\begin{equation}\label{eq:SwarmDistance1}
d = \sqrt{(x_{t}-x_{t^1})^2+(y_{t}-y_{t^1})^2}
\end{equation}

\begin{equation}\label{eq:SwarmSpeed1}
S_s = \frac{d}{n}
\end{equation}
